---
author: "Kianté A. Fernandez"
date: "5/5/2020"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load library, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(reshape2)
```


```{r yeses, include=FALSE}
#100% risk of harm 
batch.1.1 <- read.csv("../data/batch.1.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE) %>%
    select(user_id, risk, gain, no_effect, experimental_treatment_selected, trial_index, batch, Risk_Beta , Gain_Beta , Interaction_Beta, Risk_sig, Gain_sig, Interaction_sig)
batch.1 <- read.csv("../data/Cleaned_Pilot.05.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE) %>%
    select(user_id, risk, gain, no_effect, experimental_treatment_selected, trial_index, batch,  Risk_Beta , Gain_Beta , Interaction_Beta, Risk_sig, Gain_sig, Interaction_sig) %>%
    filter(batch == 2)
batch.1 <- rbind(batch.1.1, batch.1) %>% 
    filter(experimental_treatment_selected == 'Yes to treatment') 
rm(batch.1.1)

#first batch with 70%
batch.2 <- read.csv("../data/Cleaned_Pilot.05.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE) %>%
    select(user_id, risk, gain, no_effect, experimental_treatment_selected, trial_index, batch,  Risk_Beta , Gain_Beta , Interaction_Beta, Risk_sig, Gain_sig, Interaction_sig) %>%
    filter(batch == 3) %>% 
    filter(experimental_treatment_selected == 'Yes to treatment')

#Study 1 deployment
batch.3 <- read.csv("../data/Cleaned_Pilot.05.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE) %>%
    select(user_id, risk, gain, no_effect, experimental_treatment_selected, trial_index, batch,  Risk_Beta , Gain_Beta , Interaction_Beta, Risk_sig, Gain_sig, Interaction_sig) %>%
    filter(batch == 4) %>%
    filter(experimental_treatment_selected == 'Yes to treatment')

batch.total <- read.csv("../data/Cleaned_Pilot.05.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE) %>%
    select(user_id, risk, gain, no_effect,condition, experimental_treatment_selected, trial_index, batch,  Risk_Beta , Gain_Beta , Interaction_Beta, Risk_sig, Gain_sig, Interaction_sig) %>%
    filter(batch >= 3)


```

```{r summary, fig.height=10, fig.width=20, dpi= 300, echo=FALSE}

tt2 <- ttheme_default()

grid.arrange(
  tableGrob(summary(batch.1), theme=tt2),
  tableGrob(summary(batch.2), theme=tt2),
  tableGrob(summary(batch.3), theme=tt2),
  nrow=3)
```

Batch 1 is our data prior to the 70 cut off **(67 subjects)**

Batch 2 is our first data set post the 70 cut off **(34 subjects)**

Batch 3 is our data set post deployment **(61 subjects)**

\newpage

Here at side by side comparaisons of the 1st batch 2nd and 3rd batch total trial distributions.

```{r overall trial distribution for risk, fig.height=4, fig.width=12, dpi= 300,  echo=F}
#Risk
p1 <- ggplot(batch.1, aes(risk, fill = experimental_treatment_selected)) +
    geom_histogram(binwidth=5, colour="black", fill="#ee7c2e") + 
    geom_vline(aes(xintercept=mean(risk, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("Risk of Harm", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 25), limits=c(0, 500)) + ggtitle("Batch 1")+theme(plot.title = element_text(lineheight=.8, face="bold"))

p2 <- ggplot(batch.2, aes(risk, fill = experimental_treatment_selected)) +
    geom_histogram(binwidth=5, colour="black", fill="#ee7c2e") + 
    geom_vline(aes(xintercept=mean(risk, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("Risk of Harm", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 25), limits=c(0, 500))+ ggtitle("Batch 2") +theme(plot.title = element_text(lineheight=.8, face="bold"))

p3 <- ggplot(batch.3, aes(risk, fill = experimental_treatment_selected)) +
    geom_histogram(binwidth=5, colour="black", fill="#ee7c2e") + 
    geom_vline(aes(xintercept=mean(risk, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("Risk of Harm", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 25), limits=c(0, 500))+ ggtitle("Batch 3") +theme(plot.title = element_text(lineheight=.8, face="bold"))
#grid.arrange(p1, p2, p3, ncol = 3)
```

```{r gain trials, fig.height=4, fig.width=12, dpi= 300, echo=F}
#Gain
p4 <- ggplot(batch.1, aes(gain, fill = experimental_treatment_selected)) +
    geom_histogram(binwidth=5, colour="black", fill="#4673c3") + 
    geom_vline(aes(xintercept=mean(gain, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("Benifit", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 25), limits=c(0, 500))

p5 <-ggplot(batch.2, aes(gain, fill = experimental_treatment_selected)) +
    geom_histogram(binwidth=5, colour="black", fill="#4673c3") + 
    geom_vline(aes(xintercept=mean(gain, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("Benifit", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 25), limits=c(0, 500))

p6 <-ggplot(batch.3, aes(gain, fill = experimental_treatment_selected)) +
    geom_histogram(binwidth=5, colour="black", fill="#4673c3") + 
    geom_vline(aes(xintercept=mean(gain, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("Benifit", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 25), limits=c(0, 500))
#grid.arrange(p3, p4, ncol = 2)
```

```{r no effect trials, fig.height=4, fig.width=12, dpi= 300, echo=F}
#No Effect
p7 <- ggplot(batch.1, aes(no_effect, fill = experimental_treatment_selected)) +   
    geom_histogram(binwidth=5, colour="black", fill="#747474") + 
    geom_vline(aes(xintercept=mean(no_effect, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("no effect", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 50), limits=c(0, 500))

p8 <- ggplot(batch.2, aes(no_effect, fill = experimental_treatment_selected)) + 
    geom_histogram(binwidth=5, colour="black", fill="#747474") + 
    geom_vline(aes(xintercept=mean(no_effect, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("no effect", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 50), limits=c(0, 500))

p9 <- ggplot(batch.3, aes(no_effect, fill = experimental_treatment_selected)) + 
    geom_histogram(binwidth=5, colour="black", fill="#747474") + 
    geom_vline(aes(xintercept=mean(no_effect, na.rm=T)),
               color="red", linetype="dashed", size=1)+
    scale_x_continuous("no effect", breaks=seq(0, 100, 5))+
    scale_y_continuous("Count", breaks=seq(0, 500, 50), limits=c(0, 500))

#grid.arrange(p5, p6, ncol = 2)
```

```{r all distributions, fig.height=10, fig.width=12, dpi= 300}
grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,p9, ncol = 3)
```

The x axis represents the probability that the cognitive deficit either has risk(orange), gain (blue), and no effect (grey) and our Y axis is the total count of observations where an expriemental treatment was chosen. 


```{r subject wise odds of Yes, fig.height=10, fig.width=12, dpi=300, echo=F}
##Risk
p1<- ggplot(batch.1, aes(x=risk, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(risk, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("Risk of Harm", breaks=seq(0, 100, 5))+
  scale_y_continuous("density", breaks=seq(0, .10, .01), limits = c(0, .10))+
  theme(legend.position="none")+ ggtitle("Batch 1")

p2<- ggplot(batch.2, aes(x=risk, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(risk, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("Risk of Harm", breaks=seq(0, 100, 5))+
  scale_y_continuous("density", breaks=seq(0, .10, .01), limits = c(0, .10))+
  theme(legend.position="none")+ ggtitle("Batch 2")

p3<- ggplot(batch.3, aes(x=risk, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(risk, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("Risk of Harm", breaks=seq(0, 100, 5))+
  scale_y_continuous("density", breaks=seq(0, .10, .01), limits = c(0, .10))+
  theme(legend.position="none")+ ggtitle("Batch 3")

grid.arrange(p1, p2, p3)
```

```{r gain density, fig.height=10, fig.width=12, dpi=300, echo=F}
##Gain 
p1<- ggplot(batch.1, aes(x=gain, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(gain, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("Benifit", breaks=seq(0, 100, 5))+
  theme(legend.position="none") + ggtitle("Batch 1")

p2 <- ggplot(batch.2, aes(x=gain, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(gain, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("Benifit", breaks=seq(0, 100, 5))+
  theme(legend.position="none") + ggtitle("Batch 2")

p3 <- ggplot(batch.3, aes(x=gain, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(gain, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("Benifit", breaks=seq(0, 100, 5))+
  theme(legend.position="none") + ggtitle("Batch 3")

grid.arrange(p1, p2, p3)
```

```{r no effect density, fig.height=10, fig.width=12, dpi=300, echo=FALSE}
#No effect
p1 <- ggplot(batch.1, aes(x=no_effect, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(no_effect, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("No Effect", breaks=seq(0, 100, 5))+
  theme(legend.position="none")+ ggtitle("Batch 1")
#After filter
p2 <- ggplot(batch.2, aes(x=no_effect, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(no_effect, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("No Effect", breaks=seq(0, 100, 5))+
  theme(legend.position="none")+ ggtitle("Batch 2")

p3 <- ggplot(batch.3, aes(x=no_effect, color=user_id)) + geom_density()+
  geom_vline(aes(xintercept=mean(no_effect, na.rm=T)),             color="red", linetype="dashed", size=1)+
  scale_x_continuous("No Effect", breaks=seq(0, 100, 5))+
  theme(legend.position="none")+ ggtitle("Batch 3")

grid.arrange(p1, p2, p3)
```


```{r observation count, include= FALSE}
#How many observatoins does each subject have in each class (yes and no)?
datalist = list()
for (i in batch.total$user_id){
  x = filter(batch.total, user_id == i)
  dat = table(x$experimental_treatment_selected) #Check Class bias
  datalist[[i]] = dat # add it to your list
}
Observation_Counts = do.call(rbind, datalist)
colnames(Observation_Counts) = c('No', 'Yes')
summary(Observation_Counts)
rm(i, x,datalist, dat)
```
```{r observation tables, include=F, eval=FALSE}
library(knitr)
kable(Observation_Counts)
kable(summary(Observation_Counts))
```

\newpage


```{r betas, fig.height=5, fig.width=14, dpi=300, echo=FALSE}
# A basic box with the conditions colored
dat.1 = distinct(select(batch.1, user_id ,  Risk_Beta , Gain_Beta , Interaction_Beta))
dat.2 = distinct(select(batch.2, user_id ,  Risk_Beta , Gain_Beta , Interaction_Beta))
dat.3 = distinct(select(batch.3, user_id ,  Risk_Beta , Gain_Beta , Interaction_Beta))

dat.1 <- melt(dat.1, 
                       id = c("user_id"),
                       variable.name = "cond", 
                       value.name = "Beta")

dat.2 <- melt(dat.2, 
                       id = c("user_id"),
                       variable.name = "cond", 
                       value.name = "Beta")

dat.3 <- melt(dat.3, 
                       id = c("user_id"),
                       variable.name = "cond", 
                       value.name = "Beta")

p1 <- ggplot(dat.1, aes(x=cond, y=Beta, fill=cond)) + geom_boxplot()+
      scale_y_continuous(limits=c(-.5, 2))+ggtitle("Batch 1") +theme(plot.title = element_text(lineheight=.8, face="bold"))

p2 <- ggplot(dat.2, aes(x=cond, y=Beta, fill=cond)) + geom_boxplot()+
      scale_y_continuous(limits=c(-.5, 2))+ggtitle("Batch 2") +theme(plot.title = element_text(lineheight=.8, face="bold"))

p3 <- ggplot(dat.3, aes(x=cond, y=Beta, fill=cond)) + geom_boxplot()+
      scale_y_continuous(limits=c(-.5, 2))+ggtitle("Batch 3") +theme(plot.title = element_text(lineheight=.8, face="bold"))

grid.arrange(p1, p2, p3, ncol = 3)
```

\newpage


```{r pvalues, fig.height=5, fig.width=13, dpi=300, echo=FALSE}
dat.1 = distinct(select(batch.1, user_id, Risk_sig, Gain_sig, Interaction_sig))
dat.2 = distinct(select(batch.2, user_id, Risk_sig, Gain_sig, Interaction_sig))
dat.3 = distinct(select(batch.3, user_id, Risk_sig, Gain_sig, Interaction_sig))

dat.1 <- melt(dat.1, 
                       id = c("user_id"),
                       variable.name = "type", 
                       value.name = "sig")

dat.2 <- melt(dat.2, 
                       id = c("user_id"),
                       variable.name = "type", 
                       value.name = "sig")

dat.3 <- melt(dat.3, 
                       id = c("user_id"),
                       variable.name = "type", 
                       value.name = "sig")

#Significant plots
p1 <- ggplot(dat.1, aes(x = type, fill = as.factor(sig))) +
         geom_bar(color = 'black', stat="count", position = "dodge")+
         scale_y_continuous(limits=c(0, 110))+ggtitle("Batch 1") +theme(plot.title = element_text(lineheight=.8, face="bold"))

p2 <- ggplot(dat.2, aes(x = type, fill = as.factor(sig))) +
         geom_bar(color = 'black', stat="count", position = "dodge")+
         scale_y_continuous(limits=c(0, 110))+ggtitle("Batch 2") +theme(plot.title = element_text(lineheight=.8, face="bold"))

p3 <- ggplot(dat.3, aes(x = type, fill = as.factor(sig))) +
         geom_bar(color = 'black', stat="count", position = "dodge")+
         scale_y_continuous(limits=c(0, 110))+ggtitle("Batch 3") +theme(plot.title = element_text(lineheight=.8, face="bold"))


grid.arrange(p1, p2, p3, ncol = 3)

```

