---
title: "Data Processing and Analysis"
author: "Kianté A. Fernandez"
date: "3/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyselect)
library(magrittr)
library(ggplot2)
library(ggpubr)

files <- list.files(path = "../data/mturk_data_first_50_subjs", pattern = "*.csv", full.names = T)
pilot <- sapply(files, readr::read_csv, simplify=FALSE) 
Mpilot = bind_rows(pilot)

N = 75 #Set the min number of trials
cleanPilot = select_(Mpilot,"user_id","condition","total_trials","risk","gain","no_effect", "experimental_treatment_selected")
cleanPilot = na.omit(cleanPilot)
cleanPilot = filter(cleanPilot, total_trials >= N)
cleanPilot = mutate(cleanPilot, ratio = gain / risk)
cleanPilot$ratio = round(cleanPilot$ratio,4)
cleanPilot$condition = factor(cleanPilot$condition)
Neuroethics_Judgement = cleanPilot

rm(Mpilot, pilot, files, cleanPilot) #Clean up the environment
source("../r_docs/Multiple_plot_function.R")
```

Given what we have seen with the distributions to this point in addation to taking a look at the observation counts, I think we have a fair rationale for skewing the sampling. 

Here is a list of all pilot subjects observations for yes and no:
```{r echo=FALSE}

datalist = list()
for (i in Neuroethics_Judgement$user_id){
  x = filter(Neuroethics_Judgement, user_id == i)
  dat = table(x$experimental_treatment_selected) #Check Class bias
  datalist[[i]] = dat # add it to your list
}
Observation_Counts = do.call(rbind, datalist)
colnames(Observation_Counts) = c('No', 'Yes')
View(Observation_Counts)
rm(i, x,datalist, dat)
print(Observation_Counts)
```

To confrim, lets take a look at a single subject.

First take a look at the distribution of Harm and Gain for a single subject. 

```{r echo=FALSE}
user_id = filter(Neuroethics_Judgement, user_id == "nB8WmX4K")
sub= filter(Neuroethics_Judgement, user_id == "nB8WmX4K")
i = "nB8WmX4K"
ggplot(sub,aes(x = risk , y = gain)) + 
  geom_point(aes(color = experimental_treatment_selected), size = 2.5, alpha = .7) +
  ggtitle(paste("75 Trials Pilot Subject: ",toString(i))) +
  scale_x_continuous("Risk Probabilities", breaks=seq(0,100,5), limits=c(0, 100)) +
  scale_y_continuous("Gain Probabilities", breaks=seq(0,100,5), limits=c(0, 100)) + 
  theme(legend.position="none")
```

Okay, good enought we might say. 
```{r echo=FALSE}
print(i)
table(sub$experimental_treatment_selected)
```

Yet the subject does not have quite a large amount of yes observations.Lets take a look at some density plots. 

Here the y axis of the density plots are the probability of getting an x value between a range of x values at least that is the commonly how I have seen it defined. These are estimated using a Gaussian kernel via kernal density estimation.

```{r echo=FALSE}
p1 = ggdensity(sub, 
          main = paste("subject: ",toString(i)),
          x = "risk",
          legend.title = "",
          add = "mean", rug = TRUE,
          color = "experimental_treatment_selected", fill ="experimental_treatment_selected", palette = c("#f8766d", "#00bfc4"))
p3 = ggdensity(sub, 
          x = "gain",
          legend.title = "",
          add = "mean", rug = TRUE,
          color = "experimental_treatment_selected", fill ="experimental_treatment_selected", palette = c("#f8766d", "#00bfc4"))
p5 = ggdensity(sub, 
          x = "no_effect",
          legend.title = "",
          add = "mean", rug = TRUE,
          color = "experimental_treatment_selected", fill ="experimental_treatment_selected", palette = c("#f8766d", "#00bfc4"))

p2=gghistogram(sub, 
            x = "risk",
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 25,
            legend.title = "")
p4=gghistogram(sub, 
            x = "gain",
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 25,
            legend.title = "")
p6=gghistogram(sub, 
            x = "no_effect",
            alpha = .5,
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 25,
            legend.title = "")

multiplot(p1, p2, p3, p4, p5, p6, cols=3)
```

## A final thoughts 

* Notice how sparce our gain distribution is.
* Also notice how we have are pulling our risk distribution from the oversample of 40 to 50 percent

I will upload the plots for all the pliot subjects in the dropbox.

Thanks for letting me get some practice in markdown.
 