---
title: "Analysis ANOVA"
author: "Kianté A. Fernandez"
date: "3/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(tidyselect)
library(magrittr)
library(ggplot2)
library(ggpubr)

files <- list.files(path = "../data/mturk_data_first_50_subjs", pattern = "*.csv", full.names = T)
pilot <- sapply(files, readr::read_csv, simplify=FALSE) 
Mpilot = bind_rows(pilot)

N = 75 #Set the min number of trials
cleanPilot = select_(Mpilot,"user_id","condition","total_trials","risk","gain","no_effect", "experimental_treatment_selected")
cleanPilot = na.omit(cleanPilot)
cleanPilot = filter(cleanPilot, total_trials >= N)
cleanPilot = mutate(cleanPilot, ratio = gain / risk)
cleanPilot$ratio = round(cleanPilot$ratio,4)
cleanPilot$condition = factor(cleanPilot$condition)
Neuroethics_Judgement = cleanPilot

rm(Mpilot, pilot, files, cleanPilot) #Clean up the environment
source("../r_docs/Multiple_plot_function.R")
```

Lets start by estimating the two models, one with the interaction term, another without. 

```{r warning=FALSE}
mod3 = by(Neuroethics_Judgement, Neuroethics_Judgement$user_id, function(x) glm(experimental_treatment_selected ~ risk + gain, data = x, family = binomial(link = "logit"),control=glm.control(maxit=50)))
mod4 = by(Neuroethics_Judgement, Neuroethics_Judgement$user_id, function(x) glm(experimental_treatment_selected ~ risk + gain + risk*gain, data = x, family = binomial(link = "logit"),control=glm.control(maxit=50)))
mod5 = by(Neuroethics_Judgement, Neuroethics_Judgement$user_id, function(x) glm(experimental_treatment_selected ~ ratio, data = x, family = binomial(link = "logit"),control=glm.control(maxit=50)))

```
Here I will pick out a subject with a significant interaction for demonstration purposes. 
```{r}
summary(mod3$nB8WmX4K)
summary(mod4$nB8WmX4K)
summary(mod5$nB8WmX4K)

```
**Does the effect that the probability of worsening a deficit have on the odds of an experimental treatment option being chosen depend on the probability of curing a deficit?**
&
**Is there a signifiant difference in our models when comparing a risk and gain model to that of a ratio model?**

```{r}
anova(mod3$nB8WmX4K, mod4$nB8WmX4K, test="Chisq")
anova(mod3$nB8WmX4K, mod5$nB8WmX4K, test="Chisq")

```

####Interpretation of interaction model

Based on the model fit, we determine there is a significant interaction between risk and gain and can assume assume (at least for this subject) that risks effect on choosing an experimental treatment is dependent on the amoung of gain. 

Further for our second findings, while showing a change in the residual deviance, we fail to reject the null within this particular subject.



For more information about subjects and to play with the code yourself, [go check out the github repo](https://github.com/kiante-fernandez/RiskBenefit_Neuroethics)! 