---
title: "mixed model"
author: "Kianté Fernandez"
date: "5/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load library, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(GGally)
library(gridExtra)
library(reshape2)
library(lmerTest)
library(lme4)
library(Hmisc)
```

```{r fig.height=6, fig.width=12, dpi= 300}
cleandata <- read.csv("../data/Cleaned_Pilot.07.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE) %>%
    dplyr::select(user_id, risk, gain, no_effect,condition, experimental_treatment_selected, trial_index, sex, age, education)


p1 <- ggplot(cleandata, aes(trial_index, risk, color = experimental_treatment_selected)) +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position = "top") +
  labs(x = "", y = "Observed Risk") +
  scale_color_manual(values = c("#f8766d", "#00bfc4"))+
  scale_x_continuous("Trial Index", breaks=seq(1, 75, 1))+
  scale_y_continuous("Risk", breaks=seq(5, 50, 5))

p2 <- ggplot(cleandata, aes(trial_index, gain, color = experimental_treatment_selected)) +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position = "top") +
  labs(x = "", y = "Observed Gain") +
  scale_color_manual(values = c("#f8766d", "#00bfc4"))+
  scale_x_continuous("Trial Index", breaks=seq(1, 75, 1))+
  scale_y_continuous("Gain", breaks=seq(5, 50, 5))

ggplot(cleandata, aes(trial_index, no_effect, color = experimental_treatment_selected)) +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  theme_set(theme_bw(base_size = 10)) +
  theme(legend.position = "top") +
  labs(x = "", y = "Observed Gain") +
  scale_color_manual(values = c("#f8766d", "#00bfc4"))+
  scale_x_continuous("Trial Index", breaks=seq(1, 75, 1))+
  scale_y_continuous("No effect", breaks=seq(5, 50, 5))

grid.arrange(p1, p2, ncol = 2)

summary(cleandata)
```

Q: People who are higher in Harm will be less liklily to endorse an experiemtnal treatment

```{r}
data <- dplyr::select(cleandata, user_id, risk, gain, no_effect,condition, experimental_treatment_selected, trial_index, sex, age, education)

data$risk.c <- scale(data$risk)
data$gain.c <- scale(data$gain)
data$no_effect.c <- scale(data$no_effect)
data$age.c <- scale(data$age)
data$trial_index.c <- scale(data$trial_index)


m.base <- glmer(experimental_treatment_selected ~ trial_index + (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.risk <- glmer(experimental_treatment_selected ~ trial_index.c +  risk.c +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.gain <- glmer(experimental_treatment_selected ~ trial_index.c + gain.c +  
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.risk.gain <- glmer(experimental_treatment_selected ~ trial_index.c + risk.c + gain.c + 
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

anova(m.base, m.risk)
anova(m.base, m.gain)
anova(m.risk, m.risk.gain)
anova(m.gain, m.risk.gain)

m.0 <- glmer(experimental_treatment_selected ~ trial_index.c + risk.c + gain.c +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.1 <- glmer(experimental_treatment_selected ~ trial_index.c + risk.c + gain.c + condition +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.2 <- glmer(experimental_treatment_selected ~ trial_index.c + risk.c*gain.c + condition +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.3 <- glmer(experimental_treatment_selected ~ trial_index.c + (risk.c + gain.c + condition)^2 +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.XX <- glmer(experimental_treatment_selected ~ trial_index.c + (risk.c + gain.c + condition)^3 +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.4 <- glmer(experimental_treatment_selected ~ trial_index.c + (risk.c + gain.c + condition)^2 + age.c +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.5 <- glmer(experimental_treatment_selected ~ trial_index.c + (risk.c + gain.c + condition)^2 + age.c + sex +
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))
m.6 <- glmer(experimental_treatment_selected ~ trial_index.c + (risk.c + gain.c + condition)^2 + age.c + sex + education + 
                   (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))


m.MAX <- glmer(experimental_treatment_selected ~ trial_index*risk*gain*condition + age + sex + education + 
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))


anova(m.0,m.1,m.2,m.3,m.4,m.5,m.6)

summary(m.6)
```


```{r}
#Create categorical interpretation matrix 

##NEEDS TO BE RECODED!
contrasts.martix =  rbind(
  "Attention vs. Language"                    = c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Long Term Memory"            = c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Mood"                        = c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Motor Function"              = c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Self Control"                = c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  "Language vs. Long Term Memory"             = c(0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Mood"                         = c(0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Motor Function"               = c(0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Self Control"                 = c(0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Short Term Memory"            = c(0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Long Term Memory vs. Mood"                 = c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Motor Function"       = c(0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Self Control"         = c(0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Mood vs. Motor Function"                   = c(0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Mood vs. Self Control"                     = c(0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Mood vs. Short Term Memory"                = c(0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Motor Function vs. Self Control"           = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  "Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  #Risk
  "Risk:Attention vs. Language"                    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0),
  "Risk:Attention vs. Long Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0),
  "Risk:Attention vs. Mood"                        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
  "Risk:Attention vs. Motor Function"              = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),
  "Risk:Attention vs. Self Control"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),
  "Risk:Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
  
  "Risk:Language vs. Long Term Memory"             = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
  "Risk:Language vs. Mood"                         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0),
  "Risk:Language vs. Motor Function"               = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0),
  "Risk:Language vs. Self Control"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0),
  "Risk:Language vs. Short Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0),
 
  "Risk:Long Term Memory vs. Mood"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0),
  "Risk:Long Term Memory vs. Motor Function"       = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0),
  "Risk:Long Term Memory vs. Self Control"         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0),
  "Risk:Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0),
 
  "Risk:Mood vs. Motor Function"                   = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
  "Risk:Mood vs. Self Control"                     = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0),
  "Risk:Mood vs. Short Term Memory"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0),
 
  "Risk:Motor Function vs. Self Control"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0),
  "Risk:Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0),
  
  "Risk:Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0),
  
  #Gain
  "Gain:Attention vs. Language"                    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Long Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Mood"                        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Motor Function"              = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Self Control"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),
  "Gain:Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
  
  "Gain:Language vs. Long Term Memory"             = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Mood"                         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Motor Function"               = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Self Control"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0),
  "Gain:Language vs. Short Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0),
 
  "Gain:Long Term Memory vs. Mood"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Motor Function"       = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Self Control"         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0),
 
  "Gain:Mood vs. Motor Function"                   = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
  "Gain:Mood vs. Self Control"                     = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0),
  "Gain:Mood vs. Short Term Memory"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0),
 
  "Gain:Motor Function vs. Self Control"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0),
  "Gain:Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0),
  
  "Gain:Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0)
)

library(multcomp)

comps <- glht(m.full, contrasts.martix)

#summary(comps) #Throws a completion error for adjustment
summary(comps) 

summary(comps, test = adjusted("none")) 
#no adjustment for mutiple comparisons.
```

```{r}
#Create categorical interpretation matrix
contrasts.martix =  rbind(
  "Attention vs. Language"                    = c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Long Term Memory"            = c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Mood"                        = c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Motor Function"              = c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Self Control"                = c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  "Language vs. Long Term Memory"             = c(0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Mood"                         = c(0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Motor Function"               = c(0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Self Control"                 = c(0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Short Term Memory"            = c(0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Long Term Memory vs. Mood"                 = c(0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Motor Function"       = c(0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Self Control"         = c(0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Mood vs. Motor Function"                   = c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Mood vs. Self Control"                     = c(0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Mood vs. Short Term Memory"                = c(0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Motor Function vs. Self Control"           = c(0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  "Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  #Gain
  "Gain:Attention vs. Language"                    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Long Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Mood"                        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Motor Function"              = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Self Control"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),
  "Gain:Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
  
  "Gain:Language vs. Long Term Memory"             = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Mood"                         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Motor Function"               = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Self Control"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0),
  "Gain:Language vs. Short Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0),
 
  "Gain:Long Term Memory vs. Mood"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Motor Function"       = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Self Control"         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0),
 
  "Gain:Mood vs. Motor Function"                   = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
  "Gain:Mood vs. Self Control"                     = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0),
  "Gain:Mood vs. Short Term Memory"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0),
 
  "Gain:Motor Function vs. Self Control"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0),
  "Gain:Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0),
  
  "Gain:Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0)
)

library(multcomp)

comps <- glht(m.XX, contrasts.martix)

#summary(comps) #Throws a completion error for adjustment
summary(comps) 

summary(comps, test = adjusted("none")) 
#no adjustment for mutiple comparisons.
```
```

```{r}

m.base <- glmer(experimental_treatment_selected ~ risk + age_4 + education + sex+
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.1 <- glmer(experimental_treatment_selected ~ risk + gain + age_4 + education + sex+ 
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.2 <- glmer(experimental_treatment_selected ~ risk + gain + condition + age_4 + education + sex+ 
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.3 <- glmer(experimental_treatment_selected ~ risk*gain + condition + age_4 + education + sex +
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))

m.4 <- glmer(experimental_treatment_selected ~ risk*gain*condition + age_4 + education + sex + 
                  (1 | user_id), 
                   data = data, family = binomial, 
                   control=glmerControl(optimizer="bobyqa"))
                   
```

```{r}

contrasts.martix =  rbind(
  "Attention vs. Language"                    = c(rep(0,56)),
  "Attention vs. Long Term Memory"            = c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Mood"                        = c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Motor Function"              = c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Self Control"                = c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  "Language vs. Long Term Memory"             = c(0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Mood"                         = c(0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Motor Function"               = c(0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Self Control"                 = c(0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Language vs. Short Term Memory"            = c(0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Long Term Memory vs. Mood"                 = c(0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Motor Function"       = c(0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Self Control"         = c(0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Mood vs. Motor Function"                   = c(0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Mood vs. Self Control"                     = c(0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Mood vs. Short Term Memory"                = c(0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
 
  "Motor Function vs. Self Control"           = c(0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  "Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  "Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
  
  #Gain
  "Gain:Attention vs. Language"                    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Long Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Mood"                        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Motor Function"              = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),
  "Gain:Attention vs. Self Control"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),
  "Gain:Attention vs. Short Term Memory"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),
  
  "Gain:Language vs. Long Term Memory"             = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Mood"                         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Motor Function"               = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0,0),
  "Gain:Language vs. Self Control"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0,0),
  "Gain:Language vs. Short Term Memory"            = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0),
 
  "Gain:Long Term Memory vs. Mood"                 = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Motor Function"       = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Self Control"         = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0,0),
  "Gain:Long Term Memory vs. Short Term Memory"    = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,1,0,0,0,0,0,0),
 
  "Gain:Mood vs. Motor Function"                   = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0),
  "Gain:Mood vs. Self Control"                     = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0,0),
  "Gain:Mood vs. Short Term Memory"                = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,0,0,0,0,0),
 
  "Gain:Motor Function vs. Self Control"           = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0),
  "Gain:Motor Function vs. Short Term Memory"      = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,0,0,0,0),
  
  "Gain:Self Control vs. Short Term Memory"        = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0)
)
```





