---
title: "R Notebook"
output: html_notebook
---

Kiante Fernandez

#Main Hypotheses

1) Consistent with previous research on behavioral economics and moral decision making, we hypothesize that participants will be more psychologically risk averse to harm than gain motivated.

2) Participants risk aversion to harm will change as the cognitive domain being treated changes. Specifically, participants will be more risk averse to mood, and self-control because these are more central to self-identity.

3) Participants who are more affluent, educated, liberal, and younger will be risk seeking relative to the average risky decision making behavior observed when judging treatments for others.

- note: we need income, age, education, and political affli here. 

4) In a classification model, the proportion of benefit to harm ratio will be more predictive of whether someone chooses an experimental treatment than the benefits or risks alone. 

##Set the stage
```{r load libraries }
source("../r_docs/LoadLibraries.R")
LoadLibraries()
```

```{r Import and Transform, warning = FALSE, include=FALSE}
#files <- list.files(path = "../data/mturk_data_first_50_subjs", pattern = "*.csv", full.names = T)

files <- list.files(path = "../data/mturk_data_total_pilot", pattern = "*.csv", full.names = T)

pilot <- sapply(files, readr::read_csv, simplify=FALSE) 
Mpilot = bind_rows(pilot)

N = 75#Set the min number of trials
n = 110#Set the number of subjects 
cleanPilot = select_(Mpilot,"user_id","condition","total_trials","risk","gain","no_effect", "experimental_treatment_selected", "key_press", "rt")
cleanPilot = na.omit(cleanPilot)
cleanPilot = filter(cleanPilot, total_trials >= N)
cleanPilot = mutate(cleanPilot, ratio = gain / risk)#Gain over Risk


#cleanPilot$ratio = round(cleanPilot$ratio,4)
cleanPilot$condition = factor(cleanPilot$condition)

#write.csv(Neuroethics_Judgement,'Cleaned_Pilot.01.csv')
```


```{r survey data}
###Add Survey Data 
survey = read.csv("../data/Qualtrics Data/Qualtrics_4_13.csv", header=TRUE, comment.char="#", stringsAsFactors=TRUE)
survey = survey[,-c(1:17)]
#questions_strings = survey[1,] #Question ID's 

colnames(survey)[1]= 'user_id' 
#colnames(survey)[20]= 'Attention_Check.1' 
#colnames(survey)[37]= 'Attention_Check.2' 

survey = filter(survey, attention_check.1 == 1)
survey = filter(survey, attention_check.2 == 1)
#survey = filter(survey, attention_check.3 == 1)

#Personlity Big 5
Big5 <- cbind(survey[,38:97], survey[,"user_id"])

for (i in 1:60) {
  Big5[[i]] <- as.numeric(Big5[[i]])
}
colnames(Big5)[61]= 'user_id' 

Big5List = list(
  Extraversion <-  
    Big5[, c(1, 6, 11, 16, 21, 26, 31, 36, 41, 46, 51, 56)],
  Agreeableness <- 
    Big5[, c(2, 7, 12, 17, 22, 27, 32, 37, 42, 47, 52, 57)],
  Conscientiousness <-  
    Big5[, c(3, 8, 13, 18, 23, 28, 33, 38, 43, 48, 53, 58)],
  Negative_Emotionality <- 
    Big5[, c(4, 9, 14, 19, 24, 29, 34, 39, 44, 49, 54, 59)],
  Open_Mindedness <- 
    Big5[, c(5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60)])

Results = list()
for (i in 1:5){
  totals <- apply(Big5List[[i]], 1, sum)
  Results[[i]] = totals 
}
TEST = do.call(rbind, Results)
colnames(TEST) = survey[,"user_id"]
rownames(TEST) <- c('Extraversion','Agreeableness','Conscientiousness','Negative_Emotionality','Open_Mindedness')
TEST = as.data.frame(t(TEST))
XX <- cbind(user_id = Big5[,"user_id"], TEST)

cleanPilot = merge(cleanPilot, XX, "user_id")
rm(XX, TEST, Results,totals)

#Moral Foundations Survey
MFQ <- cbind(survey[,4:36], survey[,"user_id"])
MFQ <- MFQ[,-16]#take out attention check
colnames(MFQ)[33]= 'user_id' 

MFQList <- list(
  Harm <- MFQ[,c(1,7,12,17,23,28)],
  Fairness <- MFQ[,c(2,8,13,18,24,29)],
  Loyalty <- MFQ[,c(3,9,14,19,25,30)],
  Athority <- MFQ[,c(4,10,15,20,26,31)],
  Sancticy <- MFQ[,c(5,11,16,21,27,32)])

Results = list()
for (i in 1:5){
  totals <- apply(MFQList[[i]], 1, sum)
  Results[[i]] = totals 
}

TEST = do.call(rbind, Results)
colnames(TEST) = survey[,"user_id"]
rownames(TEST) <- c('Harm','Fairness','Loyalty','Athority','Sancticy')
TEST <-  as.data.frame(t(TEST))
XX <- cbind(user_id = MFQ[,"user_id"], TEST)

cleanPilot <-  merge(cleanPilot, XX, "user_id")
#Next Measure
Demographics <- survey[, 98:116]
#colnames(Demographics) = c('Sex','Age', 'Race/Ethnicity', 'Education', 'Religion')

#Demographics$Age <- varhandle::unfactor(Demographics$Age)
Demographics <-  cbind(Demographics, survey[1])
Demographics$sex <- as.factor(Demographics$sex) 
cleanPilot <-  merge(cleanPilot, Demographics, "user_id")

```

We can first check the RT data to see if we can ID any cases that are out of what we would expect. 
We expect people to respond no faster than 200ms

```{r RT data,}
#Check the RT data for outliers
n= 109
trial_index = data_frame(rep.int(c(1:75), n)) #MAKE SURE THIS IS EQUAL TO THE NUMBER OF SUBJECTS after attention check
colnames(trial_index)= c("trial_index")

cleanPilot = cbind(cleanPilot,trial_index)
cleanPilot$trial_index = factor(cleanPilot$trial_index)

cleanPilot = filter(cleanPilot, rt <= 60000 & rt >= 250)

cleanPilot =subset(cleanPilot, with(cleanPilot, user_id %in% names(which(table(user_id)>=N)))) #Remove Subjects who do not have 75 trials

#table(cleanPilot$user_id) Sanity Check
cleanPilot$user_id = factor(cleanPilot$user_id)
RT = select_(cleanPilot,"user_id", "rt", "trial_index")
summary(RT)
##Plots for RT 
data_long = melt(RT, 
                 id=c("user_id","trial_index"),
                 measure=c("rt"))

summary(data_long)

ggplot(data_long, aes(trial_index, value)) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data=mean_se, geom = "pointrange") +
  scale_y_continuous("RT (milliseconds)") +
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) +
  labs(title="", 
       subtitle="",
       caption="",
       x="Trial Number",
       y="RT (milliseconds)")

datalist = list()
for (i in RT$user_id){
  x = filter(RT, user_id == i)
  dat = summary(x$rt) 
  datalist[[i]] = dat # add it to your list
}

user_id = factor(names(datalist)) #creates vector of user_id's 

for (i in user_id){
  x = filter(RT, user_id == i)
  sum = summary(x)
  print(sum)
  }

rm(data_long, x, datalist, trial_index)

```



```{r merging cleaned survey and task data}
#cleanPilot = merge(cleanPilot, survey, "user_id")
#cleanPilot = merge(cleanPilot, Demographics, "user_id")

# center predictors
#we need to get the average for each subject and subtract it from each observation

Neuroethics_Judgement = cleanPilot
Neuroethics_Judgement$experimental_treatment_selected = factor(Neuroethics_Judgement$experimental_treatment_selected, labels = c("No to treatment","Yes to treatment"))

#user_id = as.character(distinct(Neuroethics_Judgement,user_id))

```


```{r observation count}
#How many observatoins does each subject have in each class (yes and no)?
datalist = list()
for (i in Neuroethics_Judgement$user_id){
  x = filter(Neuroethics_Judgement, user_id == i)
  dat = table(x$experimental_treatment_selected) #Check Class bias
  datalist[[i]] = dat # add it to your list
}
Observation_Counts = do.call(rbind, datalist)
colnames(Observation_Counts) = c('No', 'Yes')
summary(Observation_Counts)
View(Observation_Counts)
rm(i, x,datalist, dat)
```

```{r Individual subject visual data check, eval=FALSE, include=FALSE}
#Mutiple Plots
source("../r_docs/Multiple_plot_function.R")

#Individual Scatter: subject graph 
for (i in user_id){
  sub = filter(Neuroethics_Judgement, user_id == i)
  
g = ggplot(sub,aes(x = risk , y = gain)) + 
  geom_point(aes(color = experimental_treatment_selected), size = 2.5, alpha = .7) +
  ggtitle(paste("75 Trials Pilot Subject: ",toString(i))) +
  scale_x_continuous("Risk Probabilities", breaks=seq(0,100,5), limits=c(0, 100)) +
  scale_y_continuous("Gain Probabilities", breaks=seq(0,100,5), limits=c(0, 100)) + 
  theme(legend.position="none")
  
  png(filename = paste0(i , ".png"),
      width = 500, height = 372)
  print(g)
  dev.off()
}

for (i in user_id){
  sub = filter(Neuroethics_Judgement, user_id == i)
#Density Plots for risk, gain, and no effect
  p1 = ggdensity(sub, 
          main = paste("subject: ",toString(i)),
          x = "risk",
          legend.title = "",
          xticks.by = 10,
          add = "mean", rug = TRUE,
          color = "experimental_treatment_selected", 
          fill ="experimental_treatment_selected", 
          palette = c("#f8766d", "#00bfc4"))
  p3 = ggdensity(sub, 
          x = "gain",
          legend = "none",
          xticks.by = 10,
          add = "mean", rug = TRUE,
          color = "experimental_treatment_selected", 
          fill ="experimental_treatment_selected", 
          palette = c("#f8766d", "#00bfc4"))
  p5 = ggdensity(sub, 
          x = "no_effect",
          legend = "none",
          xticks.by = 10,
          add = "mean", rug = TRUE,
          color = "experimental_treatment_selected", 
          fill ="experimental_treatment_selected", 
          palette = c("#f8766d", "#00bfc4"))
#Histograms for risk, gain, and no effect
  p2=gghistogram(sub, 
            x = "risk",
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 30,
            legend = "none",
            xticks.by = 10)
  p4=gghistogram(sub, 
            x = "gain",
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 30,
            legend = "none",
            xticks.by = 10)
  p6=gghistogram(sub, 
            x = "no_effect",
            alpha = .5,
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 30, 
            legend = "none",
            xticks.by = 10)

  png(filename = paste0(i , ".png"),
    width = 1234, height = 468)
  multiplot(p1, p2, p3, p4, p5, p6, cols=3)
  dev.off()
}
#Ratio plots
for (i in user_id){
  sub = filter(Neuroethics_Judgement, user_id == i)
  
#Density plot  
  p1 = ggdensity(sub, 
               x = "ratio",
               legend.title = paste("75 Trials Pilot Subject: ",toString(i)),
               add = "mean", rug = TRUE,
               color = "experimental_treatment_selected", 
               fill ="experimental_treatment_selected", 
               palette = c("#f8766d", "#00bfc4"),
               xticks.by = 1)
#Histogram
  p2 = gghistogram(sub, 
            x = "ratio",
            alpha = .5,
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE,
            fill = "experimental_treatment_selected",  palette = c("#f8766d", "#00bfc4"),
            add_density = TRUE, bins = 200,
            legend = "none", 
            xticks.by = 1)
  
  png(filename = paste0(i , ".png"),
    width = 1234, height = 468)
  multiplot(p1, p2, cols=1)
  dev.off()
}
```

##H1
Consistent with previous research on behavioral economics and moral decision making, we hypothesize that participants will be more psychologically risk averse to harm than gain motivated.

To do so, we will fit a binary logistic regression on the task data to display the subject wise sensitivity to risk of harm above and beyond that gain motivated judgments.  

The outcome (response) variable is binary (0/1); No treatment or Yes to experimental treatment. The predictor variables of interest are the amount of risk, gain, and no_effect within each trial. 

So we are modeling the probablity of the response from know values our prdictors(log-transformed).

```{r logisitic Regression, message=FALSE, warning=FALSE}
####Logsistic Reg
center_scale <- function(x) {
    scale(x, scale = FALSE)
}

grouped_user_id <- group_by(Neuroethics_Judgement, user_id)
x = mutate(grouped_user_id, risk_c= center_scale(risk))
y = mutate(grouped_user_id, gain_c= center_scale(gain))
foo <- dplyr::select(x, risk_c)
fee <- dplyr::select(y, gain_c)

Neuroethics_Judgement <- cbind.data.frame(Neuroethics_Judgement, foo)
Neuroethics_Judgement <- cbind.data.frame(Neuroethics_Judgement, fee)

Neuroethics_Judgement <- Neuroethics_Judgement[,-43]
Neuroethics_Judgement <- Neuroethics_Judgement[,-41]
#note the above only works if the data is the correct size


subjectModel.1 = by(Neuroethics_Judgement, Neuroethics_Judgement$user_id, function(x) glm(experimental_treatment_selected ~ risk_c + gain_c, data = x, family = binomial(link = "logit"),control=glm.control(maxit=50)))

#risk_c <- risk - mean(risk) # center predictors
#gain_c <- gain - mean(gain)

subjectModel.2 = by(Neuroethics_Judgement, Neuroethics_Judgement$user_id, function(x) glm(experimental_treatment_selected ~ risk_c*gain_c, data = x, family = binomial(link = "logit"),control=glm.control(maxit=50)))

```

```{r Model comparisons}

user_id = names(subjectModel.1) #creates vector of user_id's 

#loop an anove test of the interaction on base and ratio model
datalist = list()
for (i in 1:88){
dat = anova(subjectModel.1[[i]],
            subjectModel.2[[i]],
            test="Chisq")
  datalist[[i]] = dat
}
names(datalist) = user_id

lapply(datalist, print) 
lapply(subjectModel.2, summary)

```

```{r Pseduo R^2s }
source("../r_docs/logisticPseudoR2s.R")

#loop the r^2 calculator on the fitted final model
datalist.1 = list()
for (i in 1:88){
dat = logisticPseudoR2s(subjectModel.2[[i]])
  datalist.1[[i]] = dat
}
#subjectModel.R2 <-  do.call(rbind, datalist.1)
```


```{r odds ratios}
user_id = as.factor(names(subjectModel.3)) #creates vector of user_id's 

#Compute odds ratio
datalist.2 = list()
for (i in 1:88){
dat = exp(subjectModel.2[[i]]$coefficients)
  datalist.2[[i]] = dat
}
subjectModel.OddRatios = do.call(rbind, datalist.2)

colnames(subjectModel.OddRatios)= c('Intercept', 'Risk_Beta', 'Gain_Beta', 'Interaction_Beta')

subjectModel.OddRatios <- cbind(subjectModel.OddRatios, user_id)

for (i in 1:3) {
  subjectModel.OddRatios[[i]] <- as.numeric(subjectModel.OddRatios[[i]])
}

XXXXXX = merge(subjectModel.OddRatios,  "user_id")


str(subjectModel.OddRatios)
#Coefficients Extraction

Neuroethics_Judgement= merge(Neuroethics_Judgement, subjectModel.OddRatios, "user_id")
##I cannot get my variables back into numeric form. 
```


```{r odds ratio confidence intervals, eval=FALSE, include=FALSE}
#Compute odds ratio confidence interval
#only works if values do not contain infinites...
datalist.3 = list()
for (i in 1:39){
dat = exp(confint(subjectModel.2[[i]]))
  datalist.3[[i]] = dat
}
```



```{r Model Dignostics for best fitted model}
#Diagnostics for model 2 (Residuals)

#Interpreting residuaLs

datalist.dignostics = list()
for (i in user_id){
subjectDignostics = filter(Neuroethics_Judgement, user_id == i)
  for (ii in 1:88){
    subjectDignostics$predicted.probabilities<-fitted(subjectModel.2[[ii]])
    subjectDignostics$standardized.residuals<-rstandard(subjectModel.2[[ii]])
    subjectDignostics$studentized.residuals<-rstudent(subjectModel.2[[ii]])
    subjectDignostics$dfbeta<-dfbeta(subjectModel.2[[ii]])
    subjectDignostics$dffit<-dffits(subjectModel.2[[ii]])
    subjectDignostics$leverage<-hatvalues(subjectModel.2[[ii]])
  }
    datalist.dignostics[[i]] = subjectDignostics
}

datalist.dignostics = do.call(rbind, datalist.dignostics)


#expected leverage is (k + 1)/N
 explev = 3/75
#Neuroethics_Judgement = merge(Neuroethics_Judgement,datalist.dignostics, "user_id")
summary(datalist.dignostics)

#confusionMatrix(ifelse(fitted(subjectModel.2) > .5, "No", "Yes"), d$type)$table

```


```{r plot the fitted models for each subject, eval=FALSE, include=FALSE}
#Mutiple Plots
source("../r_docs/Multiple_plot_function.R")

for (i in user_id){
  subject = filter(datalist.dignostics, user_id == i)

  ggplot(subject, aes(x=risk, y= predicted.probabilities)) + 
      stat_summary(fun = mean, geom = "line")+
         scale_x_continuous(expand = c(0,0))
  
  ggplot(subject, aes(x=gain, y= predicted.probabilities)) + 
      stat_summary(fun = mean, geom = "line")+
         scale_x_continuous(expand = c(0,0))
  
    p1 = ggplot(subject, aes(x=risk, y= predicted.probabilities)) + 
         geom_point(size = 4, alpha = .5,   position = "jitter") + 
         stat_smooth(method="glm", se=FALSE, fullrange=TRUE, 
              method.args = list(family=quasibinomial))+
         scale_x_continuous(expand = c(0,0))+
         theme(legend.position="none")

    p2 = ggplot(subject, aes(x=gain, y= predicted.probabilities)) + 
         geom_point(size = 4, alpha = .5, position = "jitter") +
         stat_smooth(method="glm", se=FALSE, fullrange=TRUE, 
              method.args = list(family=quasibinomial))+
         scale_x_continuous(expand = c(0,0))+
         theme(legend.position="none")

    p3 = ggplot(subject,aes(x = risk , y = gain)) + 
         geom_point(aes(color = experimental_treatment_selected), 
                    size = 2.5, alpha = .7, position = "jitter") +
         ggtitle(paste("75 Trials Pilot Subject: ",toString(i))) +
         scale_x_continuous("Risk Probabilities",
                            breaks=seq(0,100,5), limits=c(0, 100)) +
         scale_y_continuous("Gain Probabilities", breaks=seq(0,100,5), 
                            limits=c(0, 100)) + 
         theme(legend.position="none")

     png(filename = paste0(i , ".png"),
       width = 1234, height = 468)
     multiplot(p1, p2, p3, cols=2)
     dev.off()
}

```

```{r}

i = '01rSsifR'
for (i in user_id){
  subject = filter(datalist.dignostics, user_id == i)

 p1 <-  ggplot(subject, aes(x=risk, y= standardized.residuals)) + 
          geom_point(position = 'jitter')+
          stat_smooth(method="glm", se=FALSE, fullrange=TRUE, 
              method.args = list(family=quasibinomial))+
          scale_x_continuous(expand = c(0,0))+
          scale_y_continuous("Mean Responce (0 = No 1 = Yes)",breaks=seq(0,1,0.25), 
                            limits=c(0, 1))

  
  p2 <- ggplot(subject, aes(x=gain, y= predicted.probabilities)) + 
           stat_summary(fun = mean, geom = "line")+
          
           scale_x_continuous(expand = c(0,0))+
          scale_y_continuous("Mean Responce (0 = No 1 = Yes)",breaks=seq(0,1,0.25), 
                            limits=c(0, 1))  
   png(filename = paste0(i , ".png"),
       width = 1234, height = 468)
     multiplot(p1, p2, cols=2)
     dev.off()
}
```


```{r risk aversion}

coefficients = lapply(subjectModel.2, coef)
coefficients = do.call(rbind, coefficients)
coefficients = coefficients[,-1]#Removes intercept
#coefficients = coefficients[,3]#Removes interaction
coefficients = data.frame(coefficients)
colnames(coefficients)= c('Risk_Beta', 'Gain_Beta', 'Interaction')
coefficients$user_id = names(subjectModel.2)

coefficients = exp(coefficients)#exponetiated 


loss_aversion = mutate(coefficients, lambda = -Risk_Beta/Gain_Beta)
Neuroethics_Judgement= merge(Neuroethics_Judgement, loss_aversion, "user_id")

summary(loss_aversion)
```


##H2

Participants risk aversion to harm will change as the cognitive domain being treated changes. Specifically, participants will be more risk averse to mood, and self-control because these are more central to self-identity.

```{r drafts, eval=FALSE, include=FALSE}

 XX =  group_by(datalist.dignostics, condition)
  
  p1 = ggplot(XX, aes(x=risk, y= predicted.probabilities, color = condition)) + 
      stat_summary(fun = mean, geom = "line")+
         scale_x_continuous(expand = c(0,0))
  
  p2 = ggplot(XX, aes(x=gain, y= predicted.probabilities, color = condition)) + 
      stat_summary(fun = mean, geom = "line")+
         scale_x_continuous(expand = c(0,0))
 XX =  group_by(Neuroethics_Judgement, user_id, condition)

  ggdensity(XX,
          x = "lambda",
          legend.title = "",
          xticks.by = 10,
          add = "mean", rug = TRUE, 
          palette = c("#f8766d"))
  
gghistogram(loss_aversion, 
            x = "lambda",
            ylab = "Number of Occurrences",
            add = "mean", rug = TRUE, bins = 30)

library(reshape2)

powerpoint <- dplyr::select(Neuroethics_Judgement, user_id , condition ,  risk , gain , no_effect, experimental_treatment_selected, Risk_Beta , Gain_Beta , Interaction, lambda, trial_index)

head(powerpoint)
     
TEST = dplyr::select(Neuroethics_Judgement, user_id , condition ,  Risk_Beta , Gain_Beta , Interaction )

TEST = distinct(Neuroethics_Judgement,user_id, condition, Risk_Beta, Gain_Beta, Interaction)
TEST[,4] = as.numeric(TEST[,4])
TEST[,3] = as.numeric(TEST[,3])

TEST[,1] = as.factor(TEST[,1])


data_long = melt(TEST, 
                 id.vars=c("user_id", "condition"))

data_long[,4] = as.numeric(data_long[,4])

modTEST <- lmer(value ~ 1 + age + sex  + condition + (1 | condition), data = data_long, REML = FALSE)
summary(modTEST)

```


```{r manuscript plot drafts, eval=FALSE, include=FALSE}
#Draft of Main Box Plot Across conditions
ggplot(data_long, aes(condition, y=value, fill=variable)) +
  geom_boxplot()+
  scale_y_continuous("Beta", breaks=seq(-.3, 2,.05), limits=c(-.3, 2)) +
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) +
  labs(title="", 
       subtitle="an investigation of domain differences",
       caption="Source: CogNew",
       x="Cognitive Domian",
       y="Log Odds")

#Separate Box Plots across conditions
ggplot(data_long, aes(condition, y=value, fill=variable)) +
  geom_boxplot()+
  facet_wrap(~condition, scale="free")
```

##Testing stuff

```{r by trial model fitting, eval=FALSE, include=FALSE}

TrialMod = by(Neuroethics_Judgement, Neuroethics_Judgement$trial_index, function(x) glm(experimental_treatment_selected ~ risk + gain + ratio, data = x, family = binomial(link = "logit"),control=glm.control(maxit=50)))

```

```{r Density plots of beta per cog domain, eval=FALSE, include=FALSE}
#Density Plot for Risk, Gain,  Ratio
p1 = ggplot(TEST, aes(Risk_Beta)) +
  geom_density(aes(fill=factor(condition)), alpha=0.8) +
  scale_x_continuous("Beta", breaks=seq(-5,10,1), limits=c(-5, 10))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))


p2 = ggplot(TEST, aes(Gain_Beta)) +
  geom_density(aes(fill=factor(condition)), alpha=0.8) +
  scale_x_continuous("Beta", breaks=seq(-5,10,1), limits=c(-5, 10))+
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
```


```{r mixed effect models drafts, eval=FALSE, include=FALSE}
library(reshape2)
library(lme4)
library(lmerTest)

TEST = dplyr::select(Neuroethics_Judgement, user_id , condition , Risk_Beta , Ratio_Beta , Gain_Beta ,  Sex ,  Age ,  Education)

TEST = distinct(Neuroethics_Judgement,user_id, condition, Risk_Beta, Gain_Beta, Ratio_Beta, Ratio_Beta)

data_long = melt(TEST, id.vars=c("user_id", "condition", "age", "sex" ))


modTEST <- glmer(experimental_treatment_selected ~ 1 + risk*condition + gain*condition +
             (1 + risk*gain | user_id), data = Neuroethics_Judgement, family = binomial)

summary(modTEST)
```

```{r Testing multicollinearity, eval=FALSE, include=FALSE}
library(car)

vif(subjectModel.2)
1/vif(subjectModel.2)

cor(subject[, c("risk", "gain", "no_effect")])

cor.test(subject$risk, subject$gain)  
cor.test(subject$risk, subject$no_effect)  
cor.test(subject$gain, subject$no_effect)
```

```{r Testing the linearity of the logit, eval=FALSE, include=FALSE}

#Create the interaction of Risk with log(risk)
subject$logRisk<-log(subject$risk)*subject$risk

#Create the interaction of Gain and No Effect with their logs

subject$logGain<-log(subject$gain)*subject$gain
subject$logNo_effect<-log(subject$no_effect)*subject$no_effect

head(subject)



subjectTest.1 <- glm(experimental_treatment_selected ~ 
                       risk +
                       gain + 
                       no_effect +
                       logRisk +
                       logGain +	
                       logNo_effect, 
                     data=subject, family=binomial())
summary(subjectTest.1)
# None of the Interaction variables show significance, so linearity test passes
```

```{r users to remove}
REMOVE = c(
  "wpchz8fz",
  "tdDTyNLl",
  "CUyB01Th",
  "d9UbV0sj",
  "PiGCo5DO",
  "yCZDIVJF",
  "WUTFOue2",
  "Rp8H93tM",
  "9Z5vJ7oT",
  "esSkjqdS",
  "XNHqndg3",
  "spGR9XvT",
  "qf27dbHj",
  "y6m1AOsD",
  "hgbHHiLn",
  "Ly8mJkxP"
)

Neuroethics_Judgement %>%
      group_by(user_id)  %>%
      mutate(Neuroethics_Judgement, risk_c= risk-mean(risk)) %>%
      mutate(Neuroethics_Judgement, gain_c= gain-mean(gain))

Neuroethics_Judgement %>%
      group_by(user_id)  %>%
      mutate(risk_c= risk-mean(risk)) %>%
      mutate(gain_c= gain-mean(gain))
```
